### 2024-06-13 paper/main.tex
code, paper

\documentclass[a4paper,14pt,oneside,openany]{extarticle}

\input{preamble}
\input{newcommands}

\begin{document}
\onehalfspacing % полуторный интервал

%%% Титульный лист
\input{sections/title}
\setcounter{page}{2}

%%% Настройка размеров шрифтов
%\makeatletter
%\renewcommand\Huge{\@setfontsize\Huge{16pt}{1.5}}
%\renewcommand\huge{\@setfontsize\huge{18pt}{1.5}}
%\renewcommand\Large{\@setfontsize\Large{16pt}{1.5}}
%\renewcommand\large{\@setfontsize\large{16pt}{1.5}}
%\makeatother

%%% Аннотация
\newpage
\input{sections/abstract}

%%% Оглавление
\newpage
\tableofcontents

%%% Введение
\newpage
\input{sections/introduction}

%%% Основная часть
\newpage
\input{sections/section1}

\newpage
\input{sections/section2}

\newpage
\input{sections/section3}

%%% Заключение
\newpage
\input{sections/conclusion}

%%% Список литературы
\newpage
\bibliographystyle{unsrtnat}
\bibliography{references}

%%% Приложение
%\newpage
%\input{sections/appendix}

\end{document}